Palomar 5 Gaps

### 2024-10-21 paper/main.tex
computed linear dependence

>>>>

      From the bottom right panel we observe where the impacts happen in the meridional plane lain over Palomar 5's orbit. We see that there is a trend with $r$, the 3D galactocentric radius. The number of counts follows this equation: $N = -2.5 r + 50$ and has a pearson coefficient of -0.86, so quite strong I must say.
